Ecuador plant species IUCN data

### 2022-10-31 code/L0/L0_Ecuador_plants_IUCN.Rmd
add summary information using DataExplorer and summarytools packages

>>>>

### using DataExplorer package
```{r}
plot_str(ecuador_plants)
introduce(ecuador_plants)
plot_intro(ecuador_plants)
plot_missing(ecuador_plants)
plot_bar(ecuador_plants)
```

```{r}
plot_str(ecuador_IUCN_plant_occ)
introduce(ecuador_IUCN_plant_occ)
plot_intro(ecuador_IUCN_plant_occ)
plot_missing(ecuador_IUCN_plant_occ)
plot_bar(ecuador_IUCN_plant_occ)
```

```{r}
plot_str(ecuador_IUCN_plant_habitat)
introduce(ecuador_IUCN_plant_habitat)
plot_intro(ecuador_IUCN_plant_habitat)
plot_missing(ecuador_IUCN_plant_habitat)
plot_bar(ecuador_IUCN_plant_habitat)
```

### using summarytools package
```{r}
ecuador_plants_summary <- dfSummary(ecuador_plants, 
            na.col       = FALSE,
            style        = "multiline",
            plain.ascii  = TRUE,
            graph.magnif = .8)
print(ecuador_plants_summary, method = "render")
view(ecuador_plants_summary, file = file.path(output_path,"ecuador_plants_summary.html"))
```

```{r}
ecuador_IUCN_plant_occ_summary <- dfSummary(ecuador_IUCN_plant_occ, 
            na.col       = FALSE,
            style        = "multiline",
            plain.ascii  = TRUE,
            graph.magnif = .8)
print(ecuador_IUCN_plant_occ_summary, method = "render")
view(ecuador_IUCN_plant_occ_summary, file = file.path(output_path,"ecuador_IUCN_plant_occ_summary.html"))
```

```{r}
ecuador_IUCN_plant_habitat_summary <- dfSummary(ecuador_IUCN_plant_habitat, 
            na.col       = FALSE,
            style        = "multiline",
            plain.ascii  = TRUE,
            graph.magnif = .8)
print(ecuador_IUCN_plant_habitat_summary, method = "render")
view(ecuador_IUCN_plant_habitat_summary, file = file.path(output_path,"ecuador_IUCN_plant_habitat_summary.html"))
```
